%-------------------------
% Resume in Latex
% Author : Unmesh Gundecha
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}
\usepackage{multicol}

%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

% Custom list environment for zero space
\newlist{compactitemize}{itemize}{1}
\setlist[compactitemize]{
    label=\textbullet,
    nosep,           % Removes all vertical spacing
    leftmargin=1.5em,
    rightmargin=0pt,
    before=\vspace{-1.5\baselineskip}, % Adjust based on needs
    after=\vspace{-0.5\baselineskip}
}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Unmesh Gundecha} \\ \vspace{1pt}
    \small PHONESECTIONPLACEHOLDER\href{mailto:upgundecha@gmail.com}{\underline{upgundecha@gmail.com}} $|$ 
    \href{https://linkedin.com/in/upgundecha}{\underline{linkedin.com/in/upgundecha}} $|$
    \href{https://github.com/upgundecha}{\underline{github.com/upgundecha}}
\end{center}

%-----------PROFESSIONAL SUMMARY-----------
\section{Professional Summary}
  \resumeSubHeadingListStart
    \resumeSubItem{Platform Engineering leader with 20+ years of experience building large-scale developer platforms, cloud infrastructure, and DevOps ecosystems for global financial institutions. Currently leading multi-cloud platform engineering at Standard Chartered Bank, enabling secure, compliant cloud adoption across 15+ markets and powering digital, data, and AI workloads.}
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
    {Head, Platform Engineering}{Oct 2024 -- Present}
    {Standard Chartered Bank}{Singapore}
    \resumeItemListStart
      \resumeItem{Own engineering execution of enterprise cloud platform (AWS, Azure, Databricks) supporting core banking, payments, AI and analytics workloads across 15+ markets.}
      \resumeItem{Automated multi-cloud landing zones enabling secure, compliant deployment of Tier-1 workloads with standardized identity, networking, observability, and governance controls.}
      \resumeItem{Built internal developer platforms providing self-service infrastructure (IaC, Kubernetes, databases, networking), reducing application onboarding from weeks to hours while maintaining regulatory guardrails.}
      \resumeItem{Established engineering excellence and reliability scorecards, improving CI/CD stability, release quality, and production resilience across the application estate.}
      \resumeItem{Executed FinOps and capacity optimization, delivering multi-million USD annual savings through intelligent workload placement, autoscaling, and reserved capacity strategies.}
      \resumeItem{Implemented AI-assisted engineering (internal cloud and DevOps Copilot) to improve developer productivity, compliance adherence, and incident troubleshooting. }
    \resumeItemListEnd
    
    \resumeSubheading
    {Technology Lead – CI/CD \& Developer Platforms}{Nov 2021 -- Oct 2024}
    {Standard Chartered Bank}{Singapore}
    \resumeItemListStart
        \resumeItem{Managed one of the largest Azure DevOps enterprise implementations globally, supporting 1,200+ business applications, 35K+ repositories, and 60K+ users.}
        \resumeItem{Consolidated fragmented CI/CD tooling, reducing operational complexity and achieving ~35\% reduction in platform operating costs.}
        \resumeItem{Embedded security, risk, and compliance controls by design into pipelines, enabling secure-by-default software delivery across global teams.}
        \resumeItem{Built custom platform extensions and automation using Python, JavaScript, React, and Node.js for onboarding, RBAC, policy enforcement, and release validation.}
        \resumeItem{Implemented an AI-driven engineering Copilot integrated with enterprise knowledge bases, delivering measurable improvements in developer productivity and issue resolution.}
        \resumeItem{As a product owner, led the pilot and onboarding of GitHub Copilot for 3K users in the bank.}
    \resumeItemListEnd
  
    \resumeSubheading
      {Head, DevSecOps \& Automation}{Aug 2018 -- Oct 2021}
      {Standard Chartered Bank}{Singapore}
      \resumeItemListStart
        \resumeItem{Led DevSecOps \& SRE transformation across 200+ applications, improving uptime, observability, and operational maturity.}
        \resumeItem{Introduced reliability engineering practices that reduced operational toil and improved incident response effectiveness.}
        \resumeItem{Played a key engineering leadership role in the delivery of digital and virtual banking platforms in Singapore and Hong Kong.}
        \resumeItem{Established enterprise DevSecOps standards integrating security scanning, compliance controls, and automated policy enforcement across CI/CD pipelines.}
    \resumeItemListEnd
    
    \resumeSubheading
      {Vice President – Portfolio Lead, DevOps \& Automation}{Sept 2013 -- Aug 2018}
      {Barclays}{Pune, India}
      \resumeItemListStart
        \resumeItem{Managed DevOps transformation for central compliance and legal technology platforms, reducing end-to-end delivery cycles from 12 weeks to 4 weeks.}
        \resumeItem{Guided global DevOps and automation strategy for Barclaycard, delivering £2M+ annual savings through efficiency gains, tooling rationalization, and vendor optimization.}
        \resumeItem{Established shared engineering platforms to improve reuse, transparency, and delivery consistency across teams}
    \resumeItemListEnd

    \resumeSubheading
      {Head of Quality Engineering}{Oct 2006 -- Sept 2013}
      {SunGard}{Pune, India}
      \resumeItemListStart
        \resumeItem{Directed the Quality Engineering team for SunGard Adaptive, a premier market and risk management solution in the financial services industry.}
        \resumeItem{Defined and implemented QA automation framework, tools, test automation strategies, and release quality gates across a complex financial software estate.}
        \resumeItem{Drove adoption of automated testing practices, significantly reducing regression cycles and improving release confidence.}
    \resumeItemListEnd

    \resumeSubheading
      {Earlier Career}{2003 -- 2006}
      {}{Pune, India}
      \resumeItemListStart
        \resumeItem{Tech Lead at VeriSoft Info Systems and Software Developer at WorldNet Technologies — led development of travel booking and point-of-sale retail applications, managing full SDLC across both roles.}
    \resumeItemListEnd

    % \resumeSubheading
    %   {Artificial Intelligence Research Assistant}{May 2019 -- July 2019}
    %   {Southwestern University}{Georgetown, TX}
    %   \resumeItemListStart
    %     \resumeItem{Explored methods to generate video game dungeons based off of \emph{The Legend of Zelda}}
    %     \resumeItem{Developed a game in Java to test the generated dungeons}
    %     \resumeItem{Contributed 50K+ lines of code to an established codebase via Git}
    %     \resumeItem{Conducted  a human subject study to determine which video game dungeon generation technique is enjoyable}
    %     \resumeItem{Wrote an 8-page paper and gave multiple presentations on-campus}
    %     \resumeItem{Presented virtually to the World Conference on Computational Intelligence}
    %   \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
    {The University of Texas at Austin - Texas McCombs School of Business}{Distance Education}
    {Post Graduate Program – AI \& Machine Learning (Business Applications)}{Jun 2024 -- Apr 2025}
    \resumeSubheading
      {The University of Pune}{Pune, India}
      {Master of Computer Management, Major in Software Engineering}{Jun 2000 -- May 2002}
    \resumeSubheading
      {The University of Pune}{Pune, India}
      {Bachelor of Commerce}{Jun 1997 -- May 2000}
    \resumeSubheading
     {NIIT}{Pune, India}
     {Programmed Network Computing Diploma (GNIIT)}{Jun 1997 -- Jun 1999}
  \resumeSubHeadingListEnd

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
    \textbf{Programming}{: Java, Python, JavaScript} \\
    \textbf{Development}{: Spring Boot, Express.js, React.js, HTML/CSS, REST, GraphQL, SQL, PostgreSQL, MSSQL} \\
     \textbf{Applied AI}{: Azure OpenAI, RAG, Multi-Agent Systems, AI Agents, Vector Databases, LangChain, Prompt Engineering, MCP} \\
     \textbf{DevOps}{: Azure DevOps, GitHub Actions, Jenkins, Git} \\
     \textbf{Infrastructure \& Tools}{: AWS, GCP, Docker, Terraform} \\
     \textbf{Domain}{: Personal \& Business Banking, Credit Cards, Compliance \& Legal technology, Retail}
    }}
 \end{itemize}

%-----------AREAS OF EXPERTISE-----------
\section{Areas of Expertise}
\begin{multicols}{3} % The '2' specifies two columns
  \begin{compactitemize}
    \item Platform Engineering
    \item AI-Assisted Engineering
    \item Enterprise CI/CD Platforms
    \item Engineering Excellence \& Productivity
    \item Enterprise Architecture
    \item Risk Management
    \item Program \& Project Management
    \item Cross-Functional Team Leadership
  \end{compactitemize}
\end{multicols}

%-----------ACTIVITIES & RECOGNITION-----------
\section{Activities \& Recognition}
\begin{itemize}[topsep=0pt, parsep=0pt, partopsep=0pt, itemsep=0pt]
  \item Author of multiple published books on test automation and software engineering practices.
  \item Frequent conference speaker on DevOps, platform engineering, and AI in software delivery.
  \item Active industry contributor through engineering leadership content and community engagement.
\end{itemize}

%-----------CERTIFICATIONS-----------
% \section{Certifications}
% \resumeItemListStart
%   \resumeItem{Natural Language Processing Nanodegree, Udacity}
%   \resumeItem{Deep Learning Specialization, DeepLearning.AI}
%   \resumeItem{Machine Learning Nanodegree, Udacity}
% \resumeItemListEnd

%-----------PROJECTS-----------
% \section{Projects}
%     \resumeSubHeadingListStart
%       \resumeProjectHeading
%           {\textbf{Gitlytics} $|$ \emph{Python, Flask, React, PostgreSQL, Docker}}{June 2020 -- Present}
%           \resumeItemListStart
%             \resumeItem{Developed a full-stack web application using with Flask serving a REST API with React as the frontend}
%             \resumeItem{Implemented GitHub OAuth to get data from user’s repositories}
%             \resumeItem{Visualized GitHub data to show collaboration}
%             \resumeItem{Used Celery and Redis for asynchronous tasks}
%           \resumeItemListEnd
%       \resumeProjectHeading
%           {\textbf{Simple Paintball} $|$ \emph{Spigot API, Java, Maven, TravisCI, Git}}{May 2018 -- May 2020}
%           \resumeItemListStart
%             \resumeItem{Developed a Minecraft server plugin to entertain kids during free time for a previous job}
%             \resumeItem{Published plugin to websites gaining 2K+ downloads and an average 4.5/5-star review}
%             \resumeItem{Implemented continuous delivery using TravisCI to build the plugin upon new a release}
%             \resumeItem{Collaborated with Minecraft server administrators to suggest features and get feedback about the plugin}
%           \resumeItemListEnd
%     \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}